chronologies

### 2017-12-20 analysis/chronos/analysis_chronologies.Rmd
change dir

---
title: "chronologies"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Feb"
output:  
  md_document:
    variant: markdown_github
bibliography: references.bib 
csl: ecology.csl
---

>>>>

---
title: "chronologies"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Feb"
output:  
  md_document:
    variant: markdown_github
bibliography: ../references.bib
csl: ../ecology.csl
---
